### 2019-03-04 report/final-report.tex
intro
typo
stuff

Maintaining software systems that manage evolving representations of
data is tedious and error prone.  In this study, we have developed
algorithms for automatically synthesizing \emph{lenses}, which are
software adaptors that convert between two different representations
of the same information~\cite{Focal2005}.  Lenses are a special form of
programs that 
guarantee so-called \emph{round-tripping properties} that ensure the
transformations are well-behaved.  Our synthesis algorithms take as
input (i) the \emph{type} of each source as a regular expression, and
(ii) a small collection of representative \emph{examples} of
the desired translation.  They produce as output different varieties of \emph{string
  lenses}.  Have investigated three specific varieties in detail: {\em
  bijective lenses}, {\em quotient
lenses} and {\em simple symmetric lenses}.  Bijective lenses address the
simplest case, when the two formats we want to convert between have exactly
the same information content, modulo rearrangement and reformatting.  
Quotient lenses apply when two
formats are ``morally'' but not technically bijective.  Examples include two
formats that differ in their use of white space or in the order of
sequences of elements.  Simple symmetric lenses allow one side or the other
to have 
information not present in the other; when converting between the
formats, defaults take the place of missing information.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{qfigs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{qfigs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run Optician and \QOpt{}
  on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  and then extending the synthesis specification to include QREs.
  (In other words, we restored them to their original state, added QREs,
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a
  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \Lens{}               & A lens \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  QRE                   & Quotient regular expression\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  \BSOpt{}              & Bijective lens synthesis algorithm\\

\end{tabular}

>>>>

Maintaining software systems that manage evolving representations of
data is tedious and error prone.  In this study, we have developed
algorithms for automatically synthesizing \emph{lenses}, which are
software adaptors that convert between two different representations
of the same information~\cite{Focal2005}.  Lenses are a special form of
programs that 
guarantee so-called \emph{round-tripping properties} that ensure the
transformations are well-behaved.  Our synthesis algorithms take as
input (i) the \emph{type} of each source as a regular expression, and
(ii) a small collection of representative \emph{examples} of
the desired translation.  They produce as output different varieties of \emph{string
  lenses}.

We have investigated three specific varieties of string lenses in detail: {\em
  bijective lenses}, {\em quotient
lenses} and {\em simple symmetric lenses}.  Bijective lenses address the
simplest case, when the two formats we want to convert between have exactly
the same information content, modulo rearrangement and reformatting.  
Quotient lenses apply when two
formats are ``morally'' but not technically bijective.  Examples include two
formats that differ in their use of white space or in the order of
sequences of elements.  Simple symmetric lenses allow one side or the other
to have 
information not present in the other; when converting between the
formats, defaults take the place of missing information.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{qfigs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{qfigs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtime measurements. In (a), we run Optician and \QOpt{}
  on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  and then extending the synthesis specification to include QREs.
  (In other words, we restored them to their original state, added QREs,
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a
  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\  
  \BSOpt{}              & Bijective lens synthesis algorithm\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
    JSON & JavaScript Object Notation---a standard file format used to
         encode data objects\\
  \Lens{}               & A lens \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  QRE                   & Quotient regular expression\\
    RDF & Resource Description Framework---used to model web resources \\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  XML & Extensible Markup Language---used in web services \\
\end{tabular}
